\LARGE \bf Object Detection-Based Behaviour using YOLO on Thymio

### 2018-06-01 paper/paper.tex
minor changes

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document
\usepackage{hyperref}
\usepackage{listings}
\usepackage{biblatex}
\bibliography{paper}
\usepackage{float}
\usepackage{amsmath}
\usepackage{graphicx}
% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\lstset{
%  basicstyle=\ttfamily,
  columns=fullflexible,
  frame=single,
  breaklines=true,
  basicstyle=\small
}

@@

To accomplish this task, we defined two PIDs, one for the linear velocity and one for the angular. The errors are $e_l$ for the linear PID and $e_a$ for the angular PID, defined as follow. We denote the front sensor set as $S_f$ and the rear sensor set as $S_r$, where each element in the set is a double representing the value from the sensor. In our case, $|S_f| = 5$ and $|S_r|=2$.
\begin{align*}
	e_l &= \sum\limits_{i=0}^{|S_f|} S_f(i) - \sum\limits_{i = 0}^{|R_f|} R_f(i) \\
	e_a &= (\sum\limits_{i=0}^{\frac{|S_f|}{2}} S_f(i) - \sum\limits_{i = \frac{|S_f|}{2} }^{|S_f|} S_f(i)) - 
	(\sum\limits_{i=0}^{\frac{|R_f|}{2}} R_f(i) - \sum\limits_{i = \frac{|R_f|}{2} }^{|R_f|} R_f(i))
\end{align*}
The linear error, $e_l$, is just the sum of all the frontal sensors values minus the rear sensors values.  The angular error is defined as the difference between each pair of sensors on the left and the right. In booth equation, we subtract the frontal values from the rear in order to invert the sign of the PID output so when there is an obstacle in front of the robot, the velocity is negative and vice-versa.

>>>>

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document
\usepackage{hyperref}
\usepackage{listings}
\usepackage{biblatex}
\bibliography{paper}
\usepackage{float}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{graphicx}
% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\lstset{
%  basicstyle=\ttfamily,
  columns=fullflexible,
  frame=single,
  breaklines=true,
  basicstyle=\small
}

@@

To accomplish this task, we defined two PIDs, one for the linear velocity and one for the angular. The errors are $e_l$ for the linear PID and $e_a$ for the angular PID, defined as follow. We denote the front sensor set as $S_f$ and the rear sensor set as $S_r$, where each element in the set is a double representing the value from the sensor. In our case the cardinalility of each set are $|S_f| = 5$ and $|S_r|=2$.
\begin{align}
	e_l &= \sum\limits_{i=0}^{|S_f|} S_f(i) - \sum\limits_{i = 0}^{|R_f|} R_f(i) \\
	e_a &= (\sum\limits_{i=0}^{\frac{|S_f|}{2}} S_f(i) - \sum\limits_{i = \frac{|S_f|}{2} }^{|S_f|} S_f(i))  \\
	&- (\sum\limits_{i=0}^{\frac{|R_f|}{2}} R_f(i) - \sum\limits_{i = \frac{|R_f|}{2} }^{|R_f|} R_f(i))  \notag
\end{align}
The linear error, $e_l$, is just the sum of all the frontal sensors values minus the rear sensors values.  The angular error is defined as the difference between each pair of sensors on the left and the right. In booth equation, we subtract the frontal values from the rear in order to invert the sign of the PID output so when there is an obstacle in front of the robot, the velocity is negative and vice-versa.
